Functional Pearl: Short and Mechanized Logical Relation for Dependent Type Theories

### 2024-02-27 paper/paper.tex
comment about nominal

The substitution operator, which takes the form $[[a {rho}]]$,
traverses the syntax of $[[a]]$ and replaces each variable $[[x]]$
with the term $[[rho x]]$. When traversing under binders (e.g. in the
$[[(\ x . a) { rho }]]$ case), we extend $[[rho]]$ to map the bound
variable $[[x]]$ to itself, protecting it from being replaced.

>>>>

The substitution operator, which takes the form $[[a {rho}]]$,
traverses the syntax of $[[a]]$ and replaces each variable $[[x]]$
with the term $[[rho x]]$. When traversing under binders (e.g. in the
$[[(\ x . a) { rho }]]$ case), we extend $[[rho]]$ to map the bound
variable $[[x]]$ to itself, protecting it from being replaced.
\scw{This substitution operation is pretty strange when it comes to the 
BVC. What variables are we allowed to use when we get to a bound variable $x$ in this function? I'd prefer if we instead had a side condition that it must be 
the case that $\rho(x) = x$ already, then we use BVC to pick such an $x$. But then we need to know that such an $x$ exists, and that isn't necessarily true.}
\scw{Maybe we should handwave here, and note that we aren't covering all of the 
details of the treatment of variable binding in the text. If readers want to understand that part, they should look at the Coq code, which uses de Bruijn indices anyways. Our goal is to convey the understanding of the Coq proof. }
